What is disputed on the web?

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
Added co-occurrence stats, which I will now remove in favor of clusters

>>>>

\subsection{Co-Occurring Nouns}
\label{pairs}

\begin{figure}
 \begin{tabular}{|ll|}
 \hline
 {\bf Noun} & {\bf Co-Occurring Nouns} \\
 \hline
{\bf obama} & president, election, health, muslim, america, interests,\\
            & care, peace, year, country, right, states, plan, palicies,\\
	    & U.S., bill, citizen, prize, democrats, policy, kenya \\
\hline
{\bf god}   & jesus, man, word, life, world, son, christ, universe \\  
\hline
{\bf iraq}  & war, weapons, destruction, mass, states, afghanistan, \\
            & saddam, bush, hussein, invasion, forces, uranium \\
 \hline
 \end{tabular}
\label{fig-pairs}
\caption{The most common co-occurring nouns}
\end{figure}
